---
title: "Permanent Portfolio"
author: "Jirong"
date: 2018-03-31
categories: ["investment"]
tags: ["investment", "finance", "asset_allocation"]
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## An all weather portfolio

Based on the literature, permanent portfolio is an investment strategy that is able to yield moderate returns and relatively low volatility. Investor is recommended to invest equally (25%) into GLD, Index, Bond and Cash and rebalance it back to this proportion on regular intervals. 

This approach is something that I'm keen to adopt for a portion of my portfolio. 

To investigate the feasibility, I simulated a portfolio starting at $300 on Nov 2004. I modified the asset allocation proportion slightly by first eliminating the cash and distributed the % amongst the following tickers,

- AGG: US Bonds
- GLD: Gold
- GSPC: SnP 500 

Note: 

- I admit that the code that I wrote here is very procedural. If I've time, I'll try to 'functionalize' the codes so that I could use it for other portfolio simulation purposes.
- The looping in the R vectorized setting is known to be super slow! If I really have time to spare, I'll convert some of the loops to Rcpp (C++). But I highly doubt so since the data is not that huge at the moment (unless I venture into tick data. Oh well, who knows).   

## Key points

On the annualized returns, it's not really fantastic. But it still returns a respectable annualized performance of 5%; 1% lower than Gold and 0.5% higher than SnP 500 over the same period.

What stands out, however, are the following performance metrics:

- In terms of draw-down, it performed remarkably well relative to a pure SnP500 portfolio. It suffered a loss of only 25% as compared to a catastrophic loss of 60% duirng the financial crisis.
- On the Sharpe Ratio (annualized returns in excess of risk-free rate per unit of volatility), it's considerably higher than GOLD and Snp500. Though it's slightly lower than AGG.

Feel free to adapt or adopt the code. You can easily substitute the stocks based on your preferred asset allocation.

## Setting up the analysis.

In this section, I downloaded stock data using quant mod. And merge the time series.
```{r}
library(quantmod)
library(ggplot2)
library(PerformanceAnalytics)
library(tidyr)
library(dplyr)
library(tibble)

# Download data-->Fix the ending date for project section
ticker1 = "GLD"
stock1 = getSymbols(ticker1,from="1900-01-01",auto.assign=F)
names(stock1) = c("open","high","low","close","volume","adj_close")
stock1 = stock1[,6]

ticker2 = "^GSPC"
stock2 = getSymbols(ticker2,from="1900-01-01",auto.assign=F)
names(stock2) = c("open","high","low","close","volume","adj_close")
stock2 = stock2[,6]

ticker3 = "AGG"
stock3 = getSymbols(ticker3,from="1900-01-01",auto.assign=F)
names(stock3) = c("open","high","low","close","volume","adj_close")
stock3 = stock3[,6]

# Merge the time series and subset NA
#These are the various time series
ticker_list = c("stock1","stock2","stock3")

#read in list. Loop through and assign variable to holder variable. Then assign it to combined list
ticker_all = get(ticker_list[1])  

#Merging in the time series
for(i in 2:length(ticker_list)){
  ticker_ind = get(ticker_list[i])
  ticker_all = merge(ticker_all,ticker_ind)  
}

names(ticker_all) = c("stock1","stock2","stock3")

```

## Running the simulation

Next, I run the simulation - By intialising 33% asset allocation in each of the asset and rebalance at the end of each year. Daily portfolio returns are then obtained throught the ROC function.  

```{r}
#Assign equal weights to each stream of returns
ticker_all = cbind(ticker_all,rowMeans(ticker_all))
ticker_all = subset(ticker_all,!is.na(ticker_all[,4]))
ticker_all = ticker_all[,-ncol(ticker_all)]

#Identify the period of rebalancing. Show the indexes
rebal_index = data.frame(index = endpoints(ticker_all,on="years")[-1])
# endpoints(ticker_all,on="quarters") 

#Merge in the indicator into ticker_all--Can't seem to merge. Will do the inefficient loop
# merge(ticker_all,rebal_index, by = "index", all = T)
ticker_all$rebal = NA
for(i in 1:nrow(rebal_index)){
  ticker_all$rebal[rebal_index$index[i]] = 1
}

ticker_all$rebal = ifelse(is.na(ticker_all$rebal),0,ticker_all$rebal)

#Create the returns for each price series
ticker_all$ret1 = ROC(ticker_all[,1])
ticker_all$ret2 = ROC(ticker_all[,2])
ticker_all$ret3 = ROC(ticker_all[,3])

#Initialise value for each stock series, with a total portfolio value
ticker_all$val1 = NA; ticker_all$val1[1] = 100
ticker_all$val2 = NA; ticker_all$val2[1] = 100
ticker_all$val3 = NA; ticker_all$val3[1] = 100

ticker_all$portfolio_val = NA
ticker_all$portfolio_val[1] = rowSums(ticker_all[1,8:10])

#Loop each row and 'compound'. Till it reaches the rebalancing date. Then reset stock value amount in that day. Take the portfolio value in t-1
for(i in 2:nrow(ticker_all)){
  
  if(as.numeric(ticker_all$rebal[i]) == 0){
    
  #During non-rebalancing days
  ticker_all$val1[i] = as.numeric(ticker_all$val1[i-1]) * (1 + as.numeric(ticker_all$ret1[i]))
  ticker_all$val2[i] = as.numeric(ticker_all$val2[i-1]) * (1 + as.numeric(ticker_all$ret2[i]))
  ticker_all$val3[i] = as.numeric(ticker_all$val3[i-1]) * (1 + as.numeric(ticker_all$ret3[i]))

  ticker_all$portfolio_val[i] = rowSums(ticker_all[i,8:10])
  
  }else{
  #During re-balancing days
  ticker_all$val1[i] = ticker_all$portfolio_val[i-1] / 3
  ticker_all$val2[i] = ticker_all$portfolio_val[i-1] / 3
  ticker_all$val3[i] = ticker_all$portfolio_val[i-1] / 3
  
  ticker_all$portfolio_val[i] = rowSums(ticker_all[i,8:10])      
  } 
}

#Generate the daily portfolio returns
ticker_all$portfolio_ret = ROC(ticker_all[,11])

```

## Portfolio Performance for the entire period
On the annualized returns, it's not really fantastic. But it still returns a respectable annualized performance of 5%; 1% lower than Gold and 0.5% higher than SnP 500 over the same period.

What stands out are the following performance metrics:

- In terms of draw-down, it performed remarkably well relative to a pure SnP500 portfolio. It suffered a loss of only 25% as compared to a loss of 60% during the financial crisis.
- On the Sharpe Ratio (annualized returns in excess of risk-free rate), it's considerably higher than GOLD and Snp500. Though it's slightly lower than AGG.

```{r}
######################################Study the portfolio returns########################################
#Carry out the portfolio return series
table.Drawdowns(ticker_all$portfolio_ret, top=10)
table.DownsideRisk(merge(ticker_all$portfolio_ret, ticker_all$ret1, ticker_all$ret2, ticker_all$ret3))
table.AnnualizedReturns(merge(ticker_all$portfolio_ret, ticker_all$ret1, ticker_all$ret2, ticker_all$ret3))
charts.PerformanceSummary(merge(ticker_all$portfolio_ret, ticker_all$ret1, ticker_all$ret2, ticker_all$ret3))
```

## Yearly Portfolio Performance

I also tabulated the yearly metrics of the portfolio to give a sense of the performance over years. 

```{r}
#####################################Study the annualized portfolio returns series#######################
#Use the rebal-indicator. Loop through the chunks
# https://www.quantmod.com/documentation/periodReturn.html
# https://rpubs.com/mohammadshadan/288218
# yearly_ret = periodReturn(ticker_all$portfolio_val
#              ,period='yearly',subset='2004::')  # returns years 2003 to present

yearly_ret = periodReturn(ticker_all$portfolio_val
                          ,period='yearly')  # returns years 2003 to present

#Inefficient way to calulate standard deviation. If it've time, I will probably optimize this
split_val = split(ticker_all$portfolio_ret, f = "years")
yearly_ret$annual_sd = sapply(X = split_val, FUN = StdDev) * sqrt(252)


getSymbols('DGS3MO',src = 'FRED')
rf = DGS3MO; rm(DGS3MO)
rf = rf["2004/2018"] 

split_val_rf = split(rf$DGS3MO, f = "years")
yearly_ret$annual_rf = sapply(X = split_val_rf, FUN = mean, na.rm = T)/100 

yearly_ret$Sharpe = (yearly_ret$yearly.returns - yearly_ret$annual_rf)/yearly_ret$annual_sd  

yearly_ret

plot(yearly_ret$yearly.returns)
plot(yearly_ret$Sharpe)
```